Meta-analysis

### 2019-10-18 05_MetaAnalysis.Rmd
Add section to look at genotype variability Add chunk to investigate the influence of rainfall on yeilds-  not complete

>>>>

#### Genotype yield variability

Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
```{r}
source("R/yield_volatility.r") #function to investigate the volatility in yields

yield_volatility(genotype_by_trial = FALSE, control_only = FALSE)
yield_volatility(genotype_by_trial = FALSE, control_only = TRUE)
yield_volatility(genotype_by_trial = FALSE, control_only = FALSE, location = "Hermitage")

yield_volatility("Crystal",control_only = TRUE)
yield_volatility("Crystal",control_only = FALSE)

yield_volatility("Jade",control_only = TRUE)
yield_volatility("Jade",control_only = FALSE, location = "Hermitage")

## Yield vs in-season rain

```{r}
experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)

rain_dat <- PM_MB_means[!is.na(PM_MB_means$planting_date),] # Which locations don't have NA for planting date
unique(as.character(rain_dat$location)) # locations with recorded planting date

rain_dat_sum <- rain_dat %>%
   group_by(trial_ref) %>%
   summarise(location = unique(location),
             planting_date = unique(as.character(planting_date))[1],
             grain_yield = mean(grain_yield.t.ha., na.rm = TRUE))

rain_dat_sum <- rain_dat_sum[order(rain_dat_sum$location),] # order them to make adding the lat long easier

rain_dat_sum$lat <- NA
rain_dat_sum$lon <- NA

# 
rain_dat_sum[rain_dat_sum$location == "Bongeen_1", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Bongeen 1 & 2",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Hermitage", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Hermitage Research Station",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Gatton", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Gatton",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Kingaroy", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Red Vale & Kingaroy Research Station",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Missen Flats", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Missen Flats",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "NGA - Premer",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Emerald", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Emerald Agricultural College",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Redvale", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Red Vale & Kingaroy Research Station",c("lat","lon")]

rain_dat_sum[rain_dat_sum$location == "Wellcamp", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "Wellcamp",c("lat","lon")]

source("R/AUS_rainfall_function.r")

# use Bomrang to find the quantaty of rain for the season and do a linear regression
